\section{experience}

\begin{entrylist}
%------------------------------------------------
\entry
{2020--Now}
{VMware Research}
{Senior Research Scientist}
{\small I lead the clocks project, which aims to democratize precision time and leverage it as a distributed primitive.
I also serve as a technical advisor to the VMware blockchain product, especially scaling the VMware Ethereum stack.}
%------------------------------------------------
\entry
{2017--2020}
{VMware Research}
{Research Scientist}
{\small I published award-winning papers with my collaborators and found a forte in extracting 
 key insights from complex research ideas. I worked on a broad range of topics including
 bridging the semantic gaps between kernel and userspace, interfaces for programmable hardware, 
 RDMA and security. }
\entry
{2015--2017}
{VMware Research}
{Postdoctoral Researcher}
{\small I lead the tech transfer of CorfuDB as open-source software with over 50 contributors into NSX, VMware's market leading multi-Billion dollar SDN product. 
CorfuDB now serves as the distributed control plane of NSX, providing a high throughput, strongly consistent fabric.}
\entry
{Winter 2015}
{VMware Research}
{Research Intern}
{\small I led the rebuild of CORFU from scratch in Java as CorfuDB, adding object support, in-memory time-travel and new transaction resolution mechanisms.}
\entry
{2011--2013}
{Microsoft Research}
{Consultant Researcher}
{\small I implemented ZooKeeper over CORFU.}
\entry
{Summer 2011}
{Microsoft Research}
{Research Intern}
{\small I built a hardware prototype of a CORFU Flash Unit using the BEE3 FPGA Platform.}
\entry
{2010--2017}
{University of California, San Diego}
{Graduate Researcher}
{\small At the Non-Volatile Systems Laboratory (NVSL), I led work on reliably erasing flash memory and reported findings to the military and other government organizations.}
\entry
{2008--2009}
{University of California, Irvine}
{Undergraduate Researcher}
{\small At the Cognitive Anteater Robotics Laboratory (CARL), I worked on an optimized version of the Izhikevich spiking neuron model on the IBM CELL.}
\entry
{2006--Now}
{Wei Enterprises}
{Independent Contractor}
{\small I build hardware and software for startups under tight deadlines. My code runs in consumer products all over the world.}
%------------------------------------------------
%------------------------------------------------
\end{entrylist}